\documentclass{sig-alternate-10pt}

\special{papersize=8.5in,11in}
\setlength{\pdfpageheight}{\paperheight}
\setlength{\pdfpagewidth}{\paperwidth}

\usepackage{url}
\usepackage{graphicx, color}
\usepackage[font=small,labelfont=bf]{caption}
\usepackage[subrefformat=parens]{subcaption}
\usepackage{amsmath}
\usepackage{subcaption}
\usepackage{algorithm}
\usepackage{multirow}
\usepackage[noend]{algpseudocode}
\usepackage{enumerate}
\usepackage{arydshln}
\usepackage{diagbox}
\usepackage{comment}
\usepackage{amssymb}
\usepackage[utf8]{inputenc}
\usepackage{cleveref}
\usepackage{listings}

%\pagestyle{plain}

\def\eg{\textit{e.g.}}
\def\ie{\textit{i.e.}}
\def\nfactor{\textit{NFActor}}

\begin{document}

\title{\Large \bf NFActor: A Distributed Actor Framework for Building Resillient NFV Systems}

\author{
Paper \#44, xx pages
}

\maketitle

\begin{abstract}

The trend of Network Function Virtualization is critical to ease the maintenance of complicated network functions (NFs). Unfortunately, few NFV systems have achieved a fully resilient way to maintain network functions, as most of existing NFV systems only achieve per-NF management. Per-NF management brings several key problems, for instance, during critical version update to NF software, the NF instance usually needs to be shutdown, therefore compromising the flexibility and reliability of NFV system. To solve this problems and accomplish a truly resilient way when maintaining NFs, future NFV systems should also provide efficient and fine-grained per-flow management, on top of which we can implement dynamic flow migration and reliable flow replication.

In this paper, we propose a new architecture called NFActor framework, which uses actor programming model to provide a transparent, scalable and efficient per-flow management. Different from existing works, any NFs implemented using the API provided by NFActor framework could be transparently integrated with the flow management. The flow management in NFActor framework is fully scalable, it does not need coordination from a centralized controller. NFActor framework is implemented on top of DPDK to provide efficient flow management.

NFActor NFV systems built using NFActor framework goes beyond resilience. We are able to implement scalable flow replication and several interesting applications, including live dynamic update, deduplication and reliable MPTCP subflow processing. We evaluate NFActor framework on our own cluster and show that NFActor framework could achieve an almost linear scalability, while migrating flows and recovering failed flows blazingly fast.


%The quick development of Network Function Virtualization (NFV) urges researchers to develop new functionalities for NFV system besides maximizing packet processing capacity. Among these new functionalities, resilience functionalities, such as flow migration and fault tolerance, are hard to tackle and yet very useful in production environment. However, implementing flow migration and fault tolerance requires manually modifying the source code of NF software and providing a control channel for message passing, which may be very tedious to implement and difficult to get right.

%In this paper, we present NFActor framework, a framework for building transparently resilient NFV system using actor programming model. NFActor framework provides a set of APIs for constructing NF modules and NF modules written for NFActor framework are transparently resilient. This enables implementers to focus on the core logic design of NF modules without worrying about providing interfaces to implement resilience. Due to the use of actor framework, NFActor provides a very fast migration protocol and a lightweight flow replication protocol.

%The evaluation result shows that: First, using NFActor does not incur a significant overhead when processing packet normally and NFActor framework scales well. Second, NFActor out-performs existing works on flow migration by more than 50\% in flow migration completion time. Third, NFActor achieves a consistent recovery time even under increased workload.


\end{abstract}

\input{section/introduction.tex}
\input{section/background.tex}
\input{section/overview.tex}
\input{section/module-api.tex}
\input{section/runtime-and-controller.tex}
\input{section/implementation.tex}
\input{section/evaluation.tex}
%\input{section/discussion.tex}
\input{section/related-work.tex}
\input{section/conclusion.tex}

\bibliographystyle{abbrv}
\bibliography{bibliography}

\end{document}
